MSB1015 Project

### 2024-10-14 Code/MSB1015-Project.Rmd
Update MSB1015-Project.Rmd
Added an if statement to install the required libraries

# 0. Setup
```{r setup, include=FALSE}
library(rstudioapi)
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(stringr)
library(GGally)

>>>>

# 0. Setup
```{r setup, include=FALSE}
# List of required packages
required_packages <- c("rstudioapi", "readr", "dplyr", "ggplot2", "tidyr", 
                       "stringr", "GGally", "mice", "isotree", "randomForest", 
                       "caTools", "caret", "nestedcv", "mlbench", "pbapply", 
                       "ROCR", "PRROC", "pROC", "gridExtra")

# Check and install missing packages
new_packages <- required_packages[!(required_packages %in% installed.packages()[,"Package"])]
if (length(new_packages)) {
  install.packages(new_packages)
}

# Load libraries
library(rstudioapi)
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(stringr)
library(GGally)
